Articles

### 2017-02-19 articles/articles.Rmd
correlation

>>>>

- 2017.02.14 | Why machine learning is critical to multi-touch attribution. [[MarTech](https://martechtoday.com/machine-learning-critical-multi-touch-attribution-194976?utm_source=Social&utm_medium=Share&utm_term=MTT+article+Feb&utm_content=Machine+learning+and+attribution&utm_campaign=Awareness)]
- 2017.02.05 | Unlearning descriptive statistics. [[Blog](http://debrouwere.org/2017/02/01/unlearning-descriptive-statistics/?utm_campaign=Revue%20newsletter&utm_medium=Newsletter&utm_source=revue)]
    - Caveat: multimodal distributions have more than one central or typical value, and they are trickier to describe. If you look at how tall the average adult human is, you will find a bump around 165 cm and another around 175 cm. These local maxima (modes) are useful statistics, but often it pays to prod a little deeper and see why there's more than one peak in the first place. In the case of human height, the answer is obvious: a typical adult woman is roughly 165 cm tall, a typical adult man roughly 175 cm. Once you split the data by gender, the bimodal distribution disappears.
